Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-14 draft.Rmd
Update draft.Rmd

**Practical implications:**

>>>>

**Practical implications:** Studies hoping to understand the link between job mobility and earnings growth must consider the importance of institutional frameworks. Labour market institutions shape not only the rate of job mobility in a given market, but also the rewards tied to mobility.

**Originality/value:** Studies exploring the effects of job mobility tend to focus on single country cases. The lessons from such cases are then prescribed to other countries, without acknowledging institutional differences. Our paper articulates important differences in the mobility-earnings relationship between Germany and the UK.
